Neural correlates of the deployment of spatial attention, and their modulation by repetitive movements

### 2024-07-23 manuscript.qmd
Added Bayes factor calculations

# install R packages
packagelist <- c('knitr','reticulate','osfr','bookdown','grImport','tiff','rstatix','ez') 
missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
if (length(missingpackages)>0){install.packages(missingpackages)}
toinstall <- packagelist[which(!packagelist %in% (.packages()))]
invisible(lapply(toinstall,library,character.only=TRUE))

# create python environment and install packages
if (!dir.exists('env')){
  system('python3 -m venv env')
  system('source env/bin/activate')
  system('python3 -m pip install mne numpy scikit-learn matplotlib pandas')
}
use_virtualenv('env/')

@@

@@

@@

  allCue <- matrix(0,nrow=1201,ncol=length(d))
  allTargetU <- matrix(0,nrow=1201,ncol=length(d))
  allCongIncong <- matrix(0,nrow=1201,ncol=length(d))
  allTargetB <- matrix(0,nrow=1201,ncol=length(d))
  for (s in 1:length(d)){
    decodingdata <- read.csv(d[s])
    allCue[,s] <- decodingdata$Cue
    allTargetU[,s] <- decodingdata$TargetU
    allCongIncong[,s] <- decodingdata$CongIncong
    allTargetB[,s] <- decodingdata$TargetB
  }

@@

  save(file='local/Exp1Group.RData',list=c('meandecoding','CIdecoding','meancueleft','CIcueleft','meancueright','CIcueright','meantargetleft','CItargetleft','meantargetright','CItargetright'))

@@

  d <- dir('local/processedE2',pattern='*_decoding.csv',full.names=TRUE)

  allCue <- matrix(0,nrow=1201,ncol=length(d))
  allTargetU <- matrix(0,nrow=1201,ncol=length(d))
  allCongIncong <- matrix(0,nrow=1201,ncol=length(d))
  allTargetB <- matrix(0,nrow=1201,ncol=length(d))
  allCueNostim <- matrix(0,nrow=1201,ncol=length(d))
  allCueStim <- matrix(0,nrow=1201,ncol=length(d))
  for (s in 1:length(d)){
    decodingdata <- read.csv(d[s])
    allCue[,s] <- decodingdata$Cue
    allTargetU[,s] <- decodingdata$TargetU
    allCongIncong[,s] <- decodingdata$CongIncong
    allTargetB[,s] <- decodingdata$TargetB
    allCueNostim[,s] <- decodingdata$CueNostim
    allCueStim[,s] <- decodingdata$CueStim
  }

@@

  CIdecoding <- decodingdata
  CIdecoding$Cue <- apply(allCue,1,sd)/sqrt(ncol(allCue))*1.96
  CIdecoding$TargetU <- apply(allTargetU,1,sd)/sqrt(ncol(allTargetU))*1.96
  CIdecoding$CongIncong <- apply(allCongIncong,1,sd)/sqrt(ncol(allCongIncong))*1.96
  CIdecoding$TargetB <- apply(allTargetB,1,sd)/sqrt(ncol(allTargetB))*1.96
  CIdecoding$CueNoStim <- apply(allCueNoStim,1,sd)/sqrt(ncol(allCueNoStim))*1.96
  CIdecoding$CueStim <- apply(allCueStim,1,sd)/sqrt(ncol(allCueStim))*1.96

@@

  save(file='local/Exp2Group.RData',list=c('meandecoding','CIdecoding','meancueleft','CIcueleft','meancueright','CIcueright','meantargetleft','CItargetleft','meantargetright','CItargetright'))

@@

ACCtest <- t.test(allaccuracy[,1],allaccuracy[,2],paired=TRUE)
temp <- allaccuracy[,1]-allaccuracy[,2]
ACCd <- abs(mean(temp))/sd(temp)
accdiff <- 100*(mean(allaccuracy[,1])-mean(allaccuracy[,2]))

RTtest <- t.test(allRT[,1],allRT[,2],paired=TRUE)
temp <- allRT[,1]-allRT[,2]
RTd <- abs(mean(temp))/sd(temp)
RTdiff <- 10^(mean(allRT[,2])/20)-10^(mean(allRT[,1])/20)

@@

  d <- dir('local/processedE2',pattern='_events.csv',full.names=TRUE)

  allRT <- matrix(0, nrow=length(d), 4)
  allaccuracy <- matrix(0, nrow=length(d), 4)

@@

@@

  save(file='local/Expt2resps.RData',list=c('allRT','allaccuracy'))
}

@@

accuracy <- as.vector(allaccuracy)
participant <- as.factor(rep(1:nrow(allaccuracy),4))
stimcond <- as.factor(rep(1:2,each=(2*nrow(allaccuracy))))
congruent <- as.factor(rep(1:2,each=nrow(allaccuracy),2))
accuracyaov <- data.frame(accuracy,participant,stimcond,congruent)
accAOVresults <- ezANOVA(accuracyaov, dv=accuracy, wid=participant, within=c(stimcond,congruent))

RT <- as.vector(allRT)
participant <- as.factor(rep(1:nrow(allRT),4))
stimcond <- as.factor(rep(1:2,each=(2*nrow(allRT))))
congruent <- as.factor(rep(1:2,each=nrow(allRT),2))
RTaov <- data.frame(RT,participant,stimcond,congruent)
RTAOVresults <- ezANOVA(RTaov, dv=RT, wid=participant, within=c(stimcond,congruent))

@@

@@

@@

@@

plotlims <- c(-200,1000,0,1)  
ticklocsx <- seq(-200,1000,200)    # locations of tick marks on x axis
ticklocsy <- seq(0,1,0.5)    # locations of tick marks on y axis
ticklabelsx <- ticklocsx        # set labels for x ticks
ticklabelsy <- ticklocsy    # set labels for y ticks

@@

legend(675,0.325,'Cue side',lwd=3,col='blue',box.lwd=3)

@@

legend(525,0.375,c('Target side','Target congruency'),lwd=3,col=c('black','darkgreen'),box.lwd=3)

@@

@@

legend(675,0.325,'Cue side',lwd=3,col='blue',box.lwd=3)

>>>>

# install R packages
packagelist <- c('knitr','reticulate','osfr','bookdown','grImport','tiff','rstatix','ez','readr','BayesFactor','bmp','pracma')

missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
if (length(missingpackages)>0){install.packages(missingpackages)}
toinstall <- packagelist[which(!packagelist %in% (.packages()))]
invisible(lapply(toinstall,library,character.only=TRUE))

# list of participants who report stimming (for Expt 2)
stimlist <- c(201,204,210,211,212,214,216,217,218,219,220,221,223,224)
# list of participants who report not stimming (for Expt 2)
nostimlist <- c(205,206,207,208,209,215,222,225)

# create python environment and install packages
if (processdata==2){
if (!dir.exists('env')){
  system('python3 -m venv env')
  system('source env/bin/activate')
  system('python3 -m pip install mne numpy scikit-learn matplotlib pandas')
}
use_virtualenv('env/')
}

@@

addalpha <- function(col, alpha=1){apply(sapply(col, col2rgb)/255, 2, function(x) rgb(x[1], x[2], x[3], alpha=alpha))}

@@

mkgrating <- function(regionsize, f, o, p, c){
# ported from the Matlab function, originally by Tim Meese
# generates a single component sine wave grating using the following inputs:
  # regionsize is the width of the stimulus
  # f is spatial frequency in cycles per image
  # o is orientation in degrees
  # p is phase in degrees relative to the centre of the image
  # c is contrast

p <- p*(pi/180)   # convert phase from degrees to radians
o <- o*(pi/180)   # convert orientation from degrees to radians
f <- f/regionsize # scale frequency by image size
x0 <- (regionsize+1)/2  # locate centre of image
y0 <- x0

u <- f * cos(o) * 2*pi
v <- f * sin(o) * 2*pi

gridout <- meshgrid(1:regionsize,1:regionsize)   # generate x and y coordinate systems, requires the pracma package
xx <- gridout$X
yy <- gridout$Y

output <- matrix(0,nrow=regionsize,ncol=regionsize)
output <- (c * sin(u * (xx-x0) + v*(yy-y0) + p))

return(output)}

make_soft_window <- function(W,H,D=0.9){
  # Mark's function to make sine-wave gratings, ported from Matlab
  # W is width (in pixels), H is height (in pixels)
  # D is the diameter of the soft window at half height as a proportion of the width

  radius <- min(W*D/2,H*D/2)     # radius in pixels
  L <- 2*(min(W/2,H/2) - radius) # blur half-cycle
  X1 <- seq(-L/2,L/2)

  X <- (1:W) - (W/2)
  Y <- (1:H) - (H/2)
  xx <- matrix(rep(X,H),nrow=H,ncol=W,byrow=TRUE)
  yy <- t(matrix(rep(Y,W),nrow=W,ncol=H,byrow=TRUE))

  mask <- (xx^2 + yy^2)
  mask[mask<=(radius^2)] <- 1
  mask[mask>(radius^2)] <- 0

  WinKernel <- cos(X1*pi/L)  # half-cycle cosine
  convkernW <- (1:W)*0
  convkernW[(1+(W/2)-length(X1)/2):((W/2)+length(X1)/2)] <- WinKernel
  convkernH <- (1:H)*0
  convkernH[(1+(H/2)-length(X1)/2):((H/2)+length(X1)/2)] <- WinKernel
  cH <- t(apply(mask,2,convolve,convkernH))
  cH <- cH[,c((1+H/2):H,1:(H/2))]
  cW <- apply(mask,1,convolve,convkernW)
  cW <- cW[c((1+W/2):W,1:(W/2)),]
  mask <- cH * cW

  mask <- mask/max(mask)

  return(mask)}

@@

  allCue <- matrix(0,nrow=1201,ncol=length(d))
  allTargetU <- matrix(0,nrow=1201,ncol=length(d))
  allCongIncong <- matrix(0,nrow=1201,ncol=length(d))
  allTargetB <- matrix(0,nrow=1201,ncol=length(d))
  for (s in 1:length(d)){
    decodingdata <- read.csv(d[s])
    allCue[,s] <- decodingdata$Cue
    allTargetU[,s] <- decodingdata$TargetU
    allCongIncong[,s] <- decodingdata$CongIncong
    allTargetB[,s] <- decodingdata$TargetB
  }
  decodingBFs <- matrix(0,nrow=1201,ncol=4)
  for (t in 1:nrow(allCue)){
    decodingBFs[t,1] <- extractBF(ttestBF(allCue[t,],mu=0.5,nullInterval=c(0.5,Inf)))$bf[1]
    decodingBFs[t,2] <- extractBF(ttestBF(allTargetU[t,],mu=0.5,nullInterval=c(0.5,Inf)))$bf[1]
    decodingBFs[t,3] <- extractBF(ttestBF(allCongIncong[t,],mu=0.5,nullInterval=c(0.5,Inf)))$bf[1]
    decodingBFs[t,4] <- extractBF(ttestBF(allTargetB[t,],mu=0.5,nullInterval=c(0.5,Inf)))$bf[1]
  }

@@

  save(file='local/Exp1Group.RData',list=c('meandecoding','CIdecoding','meancueleft','CIcueleft','meancueright','CIcueright','meantargetleft','CItargetleft','meantargetright','CItargetright','decodingBFs'))

@@

  d <- dir('local/processedE2',pattern='*_decoding.csv',full.names=TRUE)
  d2 <- dir('local/processedE2',pattern='*_decoding.csv',full.names=FALSE)
  sublist <- as.numeric(gsub("\\D", "", d2))

  stimindices <- which(sublist %in% stimlist)
  nostimindices <- which(sublist %in% nostimlist)

  allCue <- matrix(0,nrow=1201,ncol=length(d))
  allTargetU <- matrix(0,nrow=1201,ncol=length(d))
  allCongIncong <- matrix(0,nrow=1201,ncol=length(d))
  allTargetB <- matrix(0,nrow=1201,ncol=length(d))
  allCueNostim <- matrix(0,nrow=1201,ncol=length(d))
  allCueStim <- matrix(0,nrow=1201,ncol=length(d))
  for (s in 1:length(d)){
    decodingdata <- read.csv(d[s])
    allCue[,s] <- decodingdata$Cue
    allTargetU[,s] <- decodingdata$TargetU
    allCongIncong[,s] <- decodingdata$CongIncong
    allTargetB[,s] <- decodingdata$TargetB
    allCueNostim[,s] <- decodingdata$CueNostim
    allCueStim[,s] <- decodingdata$CueStim
  }
    decodingBFs2 <- matrix(0,nrow=1201,ncol=7)
  for (t in 1:nrow(allCue)){
    decodingBFs2[t,1] <- extractBF(ttestBF(allCue[t,],mu=0.5,nullInterval=c(0.5,Inf)))$bf[1]
    decodingBFs2[t,2] <- extractBF(ttestBF(allTargetU[t,],mu=0.5,nullInterval=c(0.5,Inf)))$bf[1]
    decodingBFs2[t,3] <- extractBF(ttestBF(allCongIncong[t,],mu=0.5,nullInterval=c(0.5,Inf)))$bf[1]
    decodingBFs2[t,4] <- extractBF(ttestBF(allTargetB[t,],mu=0.5,nullInterval=c(0.5,Inf)))$bf[1]
    decodingBFs2[t,5] <- extractBF(ttestBF(allCueNostim[t,],mu=0.5,nullInterval=c(0.5,Inf)))$bf[1]
    decodingBFs2[t,6] <- extractBF(ttestBF(allCueStim[t,],mu=0.5,nullInterval=c(0.5,Inf)))$bf[1]
    decodingBFs2[t,7] <- extractBF(ttestBF(allCueStim[t,],allCueNostim[t,],paired=TRUE))$bf
  }

@@

  CIdecoding <- decodingdata
  CIdecoding$Cue <- apply(allCue,1,sd)/sqrt(ncol(allCue))*1.96
  CIdecoding$TargetU <- apply(allTargetU,1,sd)/sqrt(ncol(allTargetU))*1.96
  CIdecoding$CongIncong <- apply(allCongIncong,1,sd)/sqrt(ncol(allCongIncong))*1.96
  CIdecoding$TargetB <- apply(allTargetB,1,sd)/sqrt(ncol(allTargetB))*1.96
  CIdecoding$CueNoStim <- apply(allCueNostim,1,sd)/sqrt(ncol(allCueNostim))*1.96
  CIdecoding$CueStim <- apply(allCueStim,1,sd)/sqrt(ncol(allCueStim))*1.96

@@

  save(file='local/Exp2Group.RData',list=c('meandecoding','CIdecoding','meancueleft','CIcueleft','meancueright','CIcueright','meantargetleft','CItargetleft','meantargetright','CItargetright','decodingBFs2'))

  meandecoding <- decodingdata
  meandecoding$Cue <- rowMeans(allCue[,stimindices])
  meandecoding$TargetU <- rowMeans(allTargetU[,stimindices])
  meandecoding$CongIncong <- rowMeans(allCongIncong[,stimindices])
  meandecoding$TargetB <- rowMeans(allTargetB[,stimindices])
  meandecoding$CueNostim <- rowMeans(allCueNostim[,stimindices])
  meandecoding$CueStim <- rowMeans(allCueStim[,stimindices])

      decodingBFs2 <- matrix(0,nrow=1201,ncol=7)
      groupcomp <- matrix(0,nrow=1201,ncol=2)
  for (t in 1:nrow(allCue)){
    decodingBFs2[t,1] <- extractBF(ttestBF(allCue[t,stimindices],mu=0.5,nullInterval=c(0.5,Inf)))$bf[1]
    decodingBFs2[t,2] <- extractBF(ttestBF(allTargetU[t,stimindices],mu=0.5,nullInterval=c(0.5,Inf)))$bf[1]
    decodingBFs2[t,3] <- extractBF(ttestBF(allCongIncong[t,stimindices],mu=0.5,nullInterval=c(0.5,Inf)))$bf[1]
    decodingBFs2[t,4] <- extractBF(ttestBF(allTargetB[t,stimindices],mu=0.5,nullInterval=c(0.5,Inf)))$bf[1]
    decodingBFs2[t,5] <- extractBF(ttestBF(allCueNostim[t,stimindices],mu=0.5,nullInterval=c(0.5,Inf)))$bf[1]
    decodingBFs2[t,6] <- extractBF(ttestBF(allCueStim[t,stimindices],mu=0.5,nullInterval=c(0.5,Inf)))$bf[1]
    decodingBFs2[t,7] <- extractBF(ttestBF(allCueStim[t,stimindices],allCueNostim[t,stimindices],paired=TRUE))$bf

    groupcomp[t,1] <- extractBF(ttestBF(allCue[t,nostimindices],allCue[t,stimindices],paired=FALSE))$bf
    groupcomp[t,2] <- extractBF(ttestBF(allCongIncong[t,nostimindices],allCongIncong[t,stimindices],paired=FALSE))$bf
  }

  CIdecoding <- decodingdata
  CIdecoding$Cue <- apply(allCue[,stimindices],1,sd)/sqrt(ncol(allCue[,stimindices]))*1.96
  CIdecoding$TargetU <- apply(allTargetU[,stimindices],1,sd)/sqrt(ncol(allTargetU[,stimindices]))*1.96
  CIdecoding$CongIncong <- apply(allCongIncong[,stimindices],1,sd)/sqrt(ncol(allCongIncong[,stimindices]))*1.96
  CIdecoding$TargetB <- apply(allTargetB[,stimindices],1,sd)/sqrt(ncol(allTargetB[,stimindices]))*1.96
  CIdecoding$CueNoStim <- apply(allCueNostim[,stimindices],1,sd)/sqrt(ncol(allCueNostim[,stimindices]))*1.96
  CIdecoding$CueStim <- apply(allCueStim[,stimindices],1,sd)/sqrt(ncol(allCueStim[,stimindices]))*1.96

  meancueleft <- getcleanmean(allcueleft[stimindices,,])
  meancueright <- getcleanmean(allcueright[stimindices,,])
  meantargetleft <- getcleanmean(alltargetleft[stimindices,,])
  meantargetright <- getcleanmean(alltargetright[stimindices,,])

  CIcueleft <- getcleanCI(allcueleft[stimindices,,])
  CIcueright <- getcleanCI(allcueright[stimindices,,])
  CItargetleft <- getcleanCI(alltargetleft[stimindices,,])
  CItargetright <- getcleanCI(alltargetright[stimindices,,])

  save(file='local/Exp2GroupStim.RData',list=c('meandecoding','CIdecoding','meancueleft','CIcueleft','meancueright','CIcueright','meantargetleft','CItargetleft','meantargetright','CItargetright', 'decodingBFs2','groupcomp'))

  meandecoding <- decodingdata
  meandecoding$Cue <- rowMeans(allCue[,nostimindices])
  meandecoding$TargetU <- rowMeans(allTargetU[,nostimindices])
  meandecoding$CongIncong <- rowMeans(allCongIncong[,nostimindices])
  meandecoding$TargetB <- rowMeans(allTargetB[,nostimindices])
  meandecoding$CueNostim <- rowMeans(allCueNostim[,nostimindices])
  meandecoding$CueStim <- rowMeans(allCueStim[,nostimindices])

        decodingBFs2 <- matrix(0,nrow=1201,ncol=7)
  for (t in 1:nrow(allCue)){
    decodingBFs2[t,1] <- extractBF(ttestBF(allCue[t,nostimindices],mu=0.5,nullInterval=c(0.5,Inf)))$bf[1]
    decodingBFs2[t,2] <- extractBF(ttestBF(allTargetU[t,nostimindices],mu=0.5,nullInterval=c(0.5,Inf)))$bf[1]
    decodingBFs2[t,3] <- extractBF(ttestBF(allCongIncong[t,nostimindices],mu=0.5,nullInterval=c(0.5,Inf)))$bf[1]
    decodingBFs2[t,4] <- extractBF(ttestBF(allTargetB[t,nostimindices],mu=0.5,nullInterval=c(0.5,Inf)))$bf[1]
    decodingBFs2[t,5] <- extractBF(ttestBF(allCueNostim[t,nostimindices],mu=0.5,nullInterval=c(0.5,Inf)))$bf[1]
    decodingBFs2[t,6] <- extractBF(ttestBF(allCueStim[t,nostimindices],mu=0.5,nullInterval=c(0.5,Inf)))$bf[1]
    decodingBFs2[t,7] <- extractBF(ttestBF(allCueStim[t,nostimindices],allCueNostim[t,nostimindices],paired=TRUE))$bf
  }
  CIdecoding <- decodingdata
  CIdecoding$Cue <- apply(allCue[,nostimindices],1,sd)/sqrt(ncol(allCue[,nostimindices]))*1.96
  CIdecoding$TargetU <- apply(allTargetU[,nostimindices],1,sd)/sqrt(ncol(allTargetU[,nostimindices]))*1.96
  CIdecoding$CongIncong <- apply(allCongIncong[,nostimindices],1,sd)/sqrt(ncol(allCongIncong[,nostimindices]))*1.96
  CIdecoding$TargetB <- apply(allTargetB[,nostimindices],1,sd)/sqrt(ncol(allTargetB[,nostimindices]))*1.96
  CIdecoding$CueNoStim <- apply(allCueNostim[,nostimindices],1,sd)/sqrt(ncol(allCueNostim[,nostimindices]))*1.96
  CIdecoding$CueStim <- apply(allCueStim[,nostimindices],1,sd)/sqrt(ncol(allCueStim[,nostimindices]))*1.96

  meancueleft <- getcleanmean(allcueleft[nostimindices,,])
  meancueright <- getcleanmean(allcueright[nostimindices,,])
  meantargetleft <- getcleanmean(alltargetleft[nostimindices,,])
  meantargetright <- getcleanmean(alltargetright[nostimindices,,])

  CIcueleft <- getcleanCI(allcueleft[nostimindices,,])
  CIcueright <- getcleanCI(allcueright[nostimindices,,])
  CItargetleft <- getcleanCI(alltargetleft[nostimindices,,])
  CItargetright <- getcleanCI(alltargetright[nostimindices,,])

  save(file='local/Exp2GroupNoStim.RData',list=c('meandecoding','CIdecoding','meancueleft','CIcueleft','meancueright','CIcueright','meantargetleft','CItargetleft','meantargetright','CItargetright','decodingBFs2','groupcomp'))

@@

ACCtest <- t.test(allaccuracy[,1],allaccuracy[,2],paired=TRUE)
temp <- allaccuracy[,1]-allaccuracy[,2]
ACCd <- abs(mean(temp))/sd(temp)
accdiff <- 100*(mean(allaccuracy[,1])-mean(allaccuracy[,2]))
ACCBF <- ttestBF(allaccuracy[,1],allaccuracy[,2],paired=TRUE)

RTtest <- t.test(allRT[,1],allRT[,2],paired=TRUE)
temp <- allRT[,1]-allRT[,2]
RTd <- abs(mean(temp))/sd(temp)
RTdiff <- 10^(mean(allRT[,2])/20)-10^(mean(allRT[,1])/20)
RTBF <- ttestBF(allRT[,1],allRT[,2],paired=TRUE)

@@

  d <- dir('local/processedE2',pattern='_events.csv',full.names=TRUE)
  d2 <- dir('local/processedE2',pattern='_events.csv',full.names=FALSE)

  allRT <- matrix(0, nrow=length(d), 4)
  allaccuracy <- matrix(0, nrow=length(d), 4)
  reportsstimming <- 0*(1:length(d))
  subjIDs <- parse_number(d2)

@@

  if (sum(subjIDs[s]==stimlist)){reportsstimming[s] <- 1}

@@

  save(file='local/Expt2resps.RData',list=c('allRT','allaccuracy','reportsstimming'))
}

@@

accuracy <- as.vector(allaccuracy)
participant <- as.factor(rep(1:nrow(allaccuracy),4))
stimcond <- as.factor(rep(1:2,each=(2*nrow(allaccuracy))))
congruent <- as.factor(rep(1:2,each=nrow(allaccuracy),2))
accuracyaov <- data.frame(accuracy,participant,stimcond,congruent)
accAOVresults <- ezANOVA(accuracyaov, dv=accuracy, wid=participant, within=c(stimcond,congruent))
accAOVBF <- anovaBF(accuracy ~ stimcond * congruent + participant, data=accuracyaov, whichModels='all', whichRandom = 'participant')

RT <- as.vector(allRT)
participant <- as.factor(rep(1:nrow(allRT),4))
stimcond <- as.factor(rep(1:2,each=(2*nrow(allRT))))
congruent <- as.factor(rep(1:2,each=nrow(allRT),2))
RTaov <- data.frame(RT,participant,stimcond,congruent)
RTAOVresults <- ezANOVA(RTaov, dv=RT, wid=participant, within=c(stimcond,congruent))
RTAOVBF <- anovaBF(RT ~ stimcond * congruent + participant, data=RTaov, whichModels='all', whichRandom = 'participant')

stimaccuracy <- allaccuracy[which(reportsstimming>0),]
accuracy <- as.vector(stimaccuracy)
participant <- as.factor(rep(1:nrow(stimaccuracy),4))
stimcond <- as.factor(rep(1:2,each=(2*nrow(stimaccuracy))))
congruent <- as.factor(rep(1:2,each=nrow(stimaccuracy),2))
accuracyaovSTIM <- data.frame(accuracy,participant,stimcond,congruent)
accAOVresultsSTIM <- ezANOVA(accuracyaovSTIM, dv=accuracy, wid=participant, within=c(stimcond,congruent))
accAOVBFSTIM <- anovaBF(accuracy ~ stimcond * congruent + participant, data=accuracyaovSTIM, whichModels='all', whichRandom = 'participant')

stimRT <- allRT[which(reportsstimming>0),]
RT <- as.vector(stimRT)
participant <- as.factor(rep(1:nrow(stimRT),4))
stimcond <- as.factor(rep(1:2,each=(2*nrow(stimRT))))
congruent <- as.factor(rep(1:2,each=nrow(stimRT),2))
RTaovSTIM <- data.frame(RT,participant,stimcond,congruent)
RTAOVresultsSTIM <- ezANOVA(RTaovSTIM, dv=RT, wid=participant, within=c(stimcond,congruent))
RTAOVBFSTIM <- anovaBF(RT ~ stimcond * congruent + participant, data=RTaovSTIM, whichModels='all', whichRandom = 'participant')

nostimaccuracy <- allaccuracy[which(reportsstimming==0),]
accuracy <- as.vector(nostimaccuracy)
participant <- as.factor(rep(1:nrow(nostimaccuracy),4))
stimcond <- as.factor(rep(1:2,each=(2*nrow(nostimaccuracy))))
congruent <- as.factor(rep(1:2,each=nrow(nostimaccuracy),2))
accuracyaovNOSTIM <- data.frame(accuracy,participant,stimcond,congruent)
accAOVresultsNOSTIM <- ezANOVA(accuracyaovNOSTIM, dv=accuracy, wid=participant, within=c(stimcond,congruent))
accAOVBFnoSTIM <- anovaBF(accuracy ~ stimcond * congruent + participant, data=accuracyaovNOSTIM, whichModels='all', whichRandom = 'participant')

nostimRT <- allRT[which(reportsstimming==0),]
RT <- as.vector(nostimRT)
participant <- as.factor(rep(1:nrow(nostimRT),4))
stimcond <- as.factor(rep(1:2,each=(2*nrow(nostimRT))))
congruent <- as.factor(rep(1:2,each=nrow(nostimRT),2))
RTaovNOSTIM <- data.frame(RT,participant,stimcond,congruent)
RTAOVresultsNOSTIM <- ezANOVA(RTaovNOSTIM, dv=RT, wid=participant, within=c(stimcond,congruent))
RTAOVBFnoSTIM <- anovaBF(RT ~ stimcond * congruent + participant, data=RTaovNOSTIM, whichModels='all', whichRandom = 'participant')

@@

```{r makemethodsfig}
#| include: false
#| output: false
#| warning: false

  facestim <- read.bmp('Experiment1code/facel.bmp')
  facestim <- as.raster(matrix(as.numeric(facestim),nrow=600,ncol=600)/255)

  stimenv <- make_soft_window(512,512,0.9)
  gratingstim <- mkgrating(512,8,90,1,1)
  targetL <- gratingstim*stimenv
  targetL[1:256,] <- targetL[1:256,]*0.5
  targetL[257:512,] <- targetL[257:512,]*0.6
  targetL <- (targetL + 1)/2
  targetU <- gratingstim*stimenv
  targetU[1:256,] <- targetU[1:256,]*0.6
  targetU[257:512,] <- targetU[257:512,]*0.5
  targetU <- (targetU + 1)/2

  pdf("Figures/MethodsFigure.pdf", height = 8, width = 19.2)

  par(mar=c(0.1,0.1,0.1,0.1))

  plotlims <- c(0,1.6,1/3,1)  
  plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])

  polygon(c(0,0,0.2,0.2)+0.1,c(0.8,1,1,0.8),lwd=2,col=rgb(0.5,0.5,0.5))
  rasterImage(facestim,0.25,0.65,0.45,0.85)
  polygon(c(0,0,0.2,0.2)+0.15+0.1,c(0.8,1,1,0.8)-0.15,lwd=2)
  polygon(c(0,0,0.2,0.2)+0.3+0.1,c(0.8,1,1,0.8)-0.3,lwd=2,col=rgb(0.5,0.5,0.5))
  polygon(c(0,0,0.2,0.2)+0.45+0.1,c(0.8,1,1,0.8)-0.45,lwd=2,col=rgb(0.5,0.5,0.5))
  rasterImage(targetL,0.57,0.42,0.63,0.48)

  lines(c(0.2,0.2),c(0.895,0.905))
  lines(c(0.195,0.205),c(0.9,0.9))
  lines(c(0.2,0.2)+0.3,c(0.895,0.905)-0.3)
  lines(c(0.195,0.205)+0.3,c(0.9,0.9)-0.3)
  lines(c(0.2,0.2)+0.45,c(0.895,0.905)-0.45)
  lines(c(0.195,0.205)+0.45,c(0.9,0.9)-0.45)

  arrows(0.05,0.8,0.5,0.35,lwd=4)
  text(0.26,0.56,'Time',adj=0.5,srt=-45,cex=2)
  text(0.32,0.95,'Fixation',pos=4,cex=1.5)
  text(0.47,0.8,'Cue (200ms)',pos=4,cex=1.5)
  text(0.62,0.65,'Fixation (400-600ms)',pos=4,cex=1.5)
  text(0.77,0.5,'Target (200ms)',pos=4,cex=1.5)

  polygon(c(0,0,0.2,0.2)+0.8,c(0.8,1,1,0.8),lwd=2,col=rgb(0.5,0.5,0.5))
  polygon(c(0,0,0.2,0.2)+0.15+0.8,c(0.8,1,1,0.8)-0.15,lwd=2,col=rgb(0.5,0.5,0.5))
  polygon(c(0,0,0.2,0.2)+0.3+0.8,c(0.8,1,1,0.8)-0.3,lwd=2,col=rgb(0.5,0.5,0.5))
  polygon(c(0,0,0.2,0.2)+0.45+0.8,c(0.8,1,1,0.8)-0.45,lwd=2,col=rgb(0.5,0.5,0.5))
  rasterImage(targetU,0.57+0.7,0.42,0.63+0.7,0.48)

  lines(c(0.2,0.2)+0.7,c(0.895,0.905))
  lines(c(0.195,0.205)+0.7,c(0.9,0.9))
  lines(c(0.2,0.2)+0.3+0.7,c(0.895,0.905)-0.3)
  lines(c(0.195,0.205)+0.3+0.7,c(0.9,0.9)-0.3)
  lines(c(0.2,0.2)+0.45+0.7,c(0.895,0.905)-0.45)
  lines(c(0.195,0.205)+0.45+0.7,c(0.9,0.9)-0.45)

  arrows(1.04,0.75,1.06,0.75,lwd=1.5,length=0.1)

  arrows(0.75,0.8,1.2,0.35,lwd=4)
  text(0.96,0.56,'Time',adj=0.5,srt=-45,cex=2)
  text(0.32+0.7,0.95,'Fixation',pos=4,cex=1.5)
  text(0.47+0.7,0.8,'Cue (200ms)',pos=4,cex=1.5)
  text(0.62+0.7,0.65,'Fixation (400-600ms)',pos=4,cex=1.5)
  text(0.77+0.7,0.5,'Target (200ms)',pos=4,cex=1.5)

  text(0.02,0.98,'(a)',cex=4)
  text(0.72,0.98,'(b)',cex=4)

@@

plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
title(xlab="Reaction time (ms)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)   
title(ylab="Proportion correct", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
title(main="No stimming", cex.main=1.5)

@@

plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
title(xlab="Reaction time (ms)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)   
title(ylab="Proportion correct", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
title(main="Stimming", cex.main=1.5)

@@

plotlims <- c(-200,1000,0.4,1.1)  
ticklocsx <- seq(-200,1000,200)    # locations of tick marks on x axis
ticklocsy <- seq(0.4,1,0.1)    # locations of tick marks on y axis
ticklabelsx <- ticklocsx        # set labels for x ticks
ticklabelsy <- ticklocsy    # set labels for y ticks

@@

i <- which(decodingBFs[,1]>3)
lines(meandecoding$Time[i],1.05+(0*i),lwd=3,col='yellow')
i <- which(decodingBFs[,1]>10)
lines(meandecoding$Time[i],1.05+(0*i),lwd=3,col='orange')
i <- which(decodingBFs[,1]>30)
lines(meandecoding$Time[i],1.05+(0*i),lwd=3,col='red')

legend(-200,1,'Cue side',lwd=3,col='blue',box.lwd=3,bg='white')

@@

i <- which(decodingBFs[,3]>3)
lines(meandecoding$Time[i],1.08+(0*i),lwd=3,col='yellow')
i <- which(decodingBFs[,3]>10)
lines(meandecoding$Time[i],1.08+(0*i),lwd=3,col='orange')
i <- which(decodingBFs[,3]>30)
lines(meandecoding$Time[i],1.08+(0*i),lwd=3,col='red')

i <- which(decodingBFs[,4]>3)
lines(meandecoding$Time[i],1.02+(0*i),lwd=3,col='yellow')
i <- which(decodingBFs[,4]>10)
lines(meandecoding$Time[i],1.02+(0*i),lwd=3,col='orange')
i <- which(decodingBFs[,4]>30)
lines(meandecoding$Time[i],1.02+(0*i),lwd=3,col='red')

legend(600,1,c('Target side','Target congruency'),lwd=3,col=c('black','darkgreen'),box.lwd=3)

@@

load('local/Exp2GroupStim.RData')
  stimdecoding <- meandecoding
  stimCI <- CIdecoding
  stimBFs <- decodingBFs2
load('local/Exp2GroupNoStim.RData')
  nostimdecoding <- meandecoding
  nostimCI <- CIdecoding  
  nostimBFs <- decodingBFs2

pdf("Figures/Exp2summary.pdf", height = 8, width = 12)

par(mfrow=c(3,2))

@@

polygon(meandecoding$Time[c(1:1201,1201:1)],c(meandecoding$Cue+CIdecoding$Cue, meandecoding$Cue[1201:1]-CIdecoding$Cue[1201:1]), col=addalpha('blue',0.2), border=NA)
